The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-08-10 manuscript.Rmd
update legend to reflect maps show iDigBio and OBIS records

```{r map-diversity-sampling, fig.cap='Spatial distribution of the number of samples (A) and species richness (B) for marine invertebrates based on specimen data available from iDigBio within the limits of the Exclusive Economic Zone for the continental USA. (\\#fig:map-diversity-sampling)'}
knitr::include_graphics("figures/map_diversity_sampling.pdf")
```

>>>>

```{r map-diversity-sampling, fig.cap='Spatial distribution of the number of samples (A) and species richness (B) for marine invertebrates based on records retrieved from iDigBio and OBIS within the limits of the Exclusive Economic Zone for the continental USA. (\\#fig:map-diversity-sampling)'}
knitr::include_graphics("figures/map_diversity_sampling.pdf")
```
